\cvsection{Experience}
\begin{cventries}
  \cventry
  {}{Institute of New Photoelectric Technology(Prof. Yuan Zhao)}{Harbin, China}{}{}
  \cvsubentry
    {Research assistant}
    {National Defense Basic Scientific Research: Quantum measurement technology based on ***}
    {Jan. 2017 - PRESENT}
    {}
    {
      \begin{cvitems}
        \item {Participate in the feasibility demonstration at proposal stage of the project, including the preliminary system design.}
        \item {Constructed the experimental system, produced the light source of requisite quantum state.}
      \end{cvitems} 
    }  
  \cvsubentry
    {Research assistant}
    {National Natural Science Foundation of China (61701139): Enhancing the angular resolution of micro rotation measurement by Z detection method}
    {Apr. 2016 - PRESENT}
    {}
    {
      \begin{cvitems}
        \item {Designed the measurement scheme for micro rotation measurement based on optical interferometer.}
        \item {Researched the angular resolution enhancing effect of Z detection method and the impact of experimental imperfect factors.}
        \item {Designed and implemented the experimental scheme, solved the alignment problem of weak light beams.}
      \end{cvitems} 
    }  
  \cvsubentry
    {Researcher}
    {Undergraduate research: Enhancing the estimation accuracy of Stokes parameters by quantum entanglement}
    {Dec. 2015 - Jun. 2016}
    {}
    {
      \begin{cvitems}
        \item {Developed the quantum description of measurement process performed by a polarimetry laser radar.}
        \item {Researched means of inducing quantum entanglement into polarimetroy system which aimed at enhancing the estimation accuracy of Stokes parameters.}
      \end{cvitems} 
    }
\end{cventries}