\cvsection{Publications}
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Physical Review A 96, no. 5 (2017): 053846.} % Role
    {State preparation and detector effects in quantum measurements of rotation with circular polarization-entangled photons and photon counting.} % Title
    {} % Location
    {2017} % Date(s)
    {{\setmainfont{SourceSansPro-Bold}Longzhu Cen}, Zijing Zhang, Jiandong Zhang, Shuo Li, Yifei Sun, Linyu Yan, Yuan Zhao, and Feng Wang.}

%---------------------------------------------------------
  \cventry
    {Optics Communications 403 (2017): 92-96.}
    {Improved resolution and sensitivity of angular rotation measurement using entangled coherent states.}
    {} % Location
    {2017} % Date(s)
    {Zijing Zhang, Tianyuan Qiao, Jie Song, {\setmainfont{SourceSansPro-Bold}Longzhu Cen}, Jiandong Zhang, Shuo Li, Linyu Yan, Yuan Zhao, and Feng Wang.}
    
%---------------------------------------------------------
  \cventry
    {Optics Express 25, no. 21 (2017): 24907-24916.}
    {Effects of imperfect elements on resolution and sensitivity of quantum metrology using two-mode squeezed vacuum state.}
    {} % Location
    {2017} % Date(s)
    {Jiandong Zhang, Zijing Zhang, {\setmainfont{SourceSansPro-Bold}Longzhu Cen}, Miao Yu, Shuo Li, Feng Wang, and Yuan Zhao.}
    
%---------------------------------------------------------
  \cventry
    {Chinese Physics B 26, no. 9 (2017): 094204.}
    {Super-resolution and super-sensitivity of entangled squeezed vacuum state using optimal detection strategy.}
    {} % Location
    {2017} % Date(s)
    {Jiandong Zhang, Zijing Zhang, {\setmainfont{SourceSansPro-Bold}Longzhu Cen}, Shuo Li, Yuan Zhao, and Feng Wang.}
    
%---------------------------------------------------------
  \cventry
    {Applied Physics B 123, no. 5 (2017): 148.}
    {Optimal quantum detection strategy for super-resolving angular-rotation measurement.}
    {} % Location
    {2017} % Date(s)
    {Zijing Zhang, Tianyuan Qiao, {\setmainfont{SourceSansPro-Bold}Longzhu Cen}, Jiandong Zhang, Feng Wang, and Yuan Zhao.}
    
%---------------------------------------------------------
  \cventry
    {Optics letters 41, no. 16 (2016): 3856-3859.}
    {Ultra-sensitive and super-resolving angular rotation measurement based on photon orbital angular momentum using parity measurement.}
    {} % Location
    {2016} % Date(s)
    {Zijing Zhang, Tianyuan Qiao, Kun Ma, {\setmainfont{SourceSansPro-Bold}Longzhu Cen}, Jiandong Zhang, Feng Wang, and Yuan Zhao.}
    
%---------------------------------------------------------
  \cventry
    {Optics express 24, no. 16 (2016): 18477-18484.}
    {Super-resolving angular rotation measurement using binary-outcome homodyne detection.}
    {} % Location
    {2016} % Date(s)
    {Zijing Zhang, Tianyuan Qiao, Kun Ma, Jiandong Zhang, {\setmainfont{SourceSansPro-Bold}Longzhu Cen}, Feng Wang, and Yuan Zhao.}

%---------------------------------------------------------
\end{cventries}